\documentclass[11pt,a4paper]{ctexart}
\usepackage[a4paper,margin=1.8cm]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage{array}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{fontspec}
\setmainfont{Times New Roman}

\setstretch{1.2}
\titleformat{\section}{\centering\bfseries\large}{}{0pt}{}
\titleformat{\subsection}{\bfseries\normalsize}{}{0pt}{}

\begin{document}

\begin{center}
    {\Large \textbf{Xi Jinping Thought on Socialism with Chinese Characteristics for a New Era}}
\end{center}

\section{I. Historical Background and Major Questions}

\begin{enumerate}[leftmargin=2em]
    \item \textbf{Historical background}: Great changes unseen in a century are accelerating; the great rejuvenation of the Chinese nation has entered a critical period; Chinese modernization is being comprehensively advanced; scientific socialism has shown new vitality in twenty-first-century China; and the Communist Party of China has opened a new realm through self-revolution.
    \item \textbf{The ``Two Integrations''}: Xi Jinping Thought on Socialism with Chinese Characteristics for a New Era is a major achievement in integrating the basic principles of Marxism with China's concrete realities and with China's fine traditional culture.
    \item \textbf{Major questions answered by the theory}: What kind of socialism with Chinese characteristics should be upheld and developed in the new era and how to uphold and develop it; what kind of modern socialist power should be built and how to build it; and what kind of long-ruling Marxist political party should be built and how to build it.
    \item \textbf{Main contents}: The theory can be summarized through the Ten Clarifications, the Fourteen Upholds, the achievements in thirteen aspects, and the Six Musts.
\end{enumerate}

\section{II. The Six Musts}

\begin{enumerate}[leftmargin=2em]
    \item \textbf{Putting the people first}: It is the fundamental value stance and reflects the historical materialist view of the masses.
    \item \textbf{Confidence and self-reliance}: It is an inner spiritual quality and reflects the organic unity of objective laws and subjective initiative.
    \item \textbf{Upholding fundamental principles and breaking new ground}: It is a distinctive theoretical quality and reflects the internal relation between change and continuity, as well as inheritance and development.
    \item \textbf{Problem orientation}: It is an important practical requirement and reflects the universality and objectivity of contradictions.
    \item \textbf{Systems thinking}: It is both a basic way of thinking and a working method, reflecting the principle of universal interconnection in dialectical materialism.
    \item \textbf{A global vision}: It represents the broad realm of Chinese Communists and reflects the lofty Marxist ideal of pursuing human progress and liberation.
\end{enumerate}

\section{III. Historical Position and the ``Two Establishes''}

\begin{enumerate}[leftmargin=2em]
    \item \textbf{Historical position}: Xi Jinping Thought on Socialism with Chinese Characteristics for a New Era is Marxism in contemporary China and Marxism in the twenty-first century, realizing a new leap in adapting Marxism to the Chinese context and the needs of the times.
    \item \textbf{Another historical significance}: It is a major achievement of the ``Two Integrations,'' connecting the ideological soul of Marxism with the cultural root of China's fine traditional culture.
    \item \textbf{Cultural significance}: It is a powerful embodiment of the cultural subjectivity of the Chinese nation and the essence of Chinese culture and spirit in the new era.
    \item \textbf{Guiding role}: It is the guide to action for the whole Party and the whole nation in striving for national rejuvenation and the fundamental guideline for the development of the Party and the state in the new era.
    \item \textbf{The ``Two Establishes''}: Establishing Comrade Xi Jinping's core position in the Party Central Committee and in the whole Party, and establishing the guiding position of Xi Jinping Thought on Socialism with Chinese Characteristics for a New Era.
    \item \textbf{Role of the ``Two Establishes''}: They are the decisive factors behind the historic achievements and changes in the cause of the Party and the state in the new era, and also the greatest certainty, confidence, and guarantee for the Party and the people in dealing with uncertainties.
\end{enumerate}

\section{IV. The New Era and Socialism with Chinese Characteristics}

\begin{enumerate}[leftmargin=2em]
    \item \textbf{Fundamental reason for all achievements since reform and opening up}: China has opened up the path of socialism with Chinese characteristics, formed its theoretical system, established its system, and developed its culture, all unified in the great practice of socialism with Chinese characteristics.
    \item \textbf{Connotation of the new era}: The new era is an era of carrying forward the past and opening up the future, of building a modern socialist power, of striving for a better life and common prosperity, of realizing the Chinese Dream of national rejuvenation, and of moving closer to the center of the world stage.
    \item \textbf{Significance of the new era}: It means a great leap for the Chinese nation from standing up and becoming prosperous to becoming strong; it means the renewed vitality of scientific socialism in China; and it offers a new option for countries seeking modernization while maintaining independence.
    \item \textbf{Basic theory for upholding and developing socialism with Chinese characteristics}: Marxism-Leninism, Mao Zedong Thought, Deng Xiaoping Theory, the Important Thought of Three Represents, the Scientific Outlook on Development, and Xi Jinping Thought on Socialism with Chinese Characteristics for a New Era.
    \item \textbf{Basic line}: Lead and unite the people of all ethnic groups, take economic development as the central task, uphold the Four Cardinal Principles, persist in reform and opening up, rely on self-reliance and hard work, and strive to build a prosperous, democratic, culturally advanced, harmonious, and beautiful modern socialist power.
\end{enumerate}

\section{V. The Fourteen Upholds and Strategic Layout}

\begin{enumerate}[leftmargin=2em]
    \item \textbf{The Fourteen Upholds}: Uphold the Party's leadership over all work; uphold the people-centered approach; uphold comprehensive deepening of reform; uphold the new development philosophy; uphold the people's status as masters of the country; uphold law-based governance in all respects; uphold the core socialist values; uphold safeguarding and improving people's well-being in development; uphold harmony between humanity and nature; uphold the holistic national security concept; uphold the Party's absolute leadership over the people's armed forces; uphold ``One Country, Two Systems'' and national reunification; uphold the building of a community with a shared future for mankind; and uphold full and rigorous self-governance of the Party.
    \item \textbf{Overall requirement}: Fully implement the Party's basic theory, basic line, and basic strategy.
    \item \textbf{Strategic coordination}: Coordinate the Five-sphere Integrated Plan and the Four-pronged Comprehensive Strategy.
\end{enumerate}

\section{VI. The Chinese Dream and Chinese Modernization}

\begin{enumerate}[leftmargin=2em]
    \item \textbf{Essence of the Chinese Dream}: National prosperity, national rejuvenation, and people's happiness.
    \item \textbf{Main features of Chinese modernization}: Modernization of a huge population, modernization for common prosperity, modernization balancing material and spiritual civilization, modernization with harmony between humanity and nature, and modernization following the path of peaceful development.
    \item \textbf{The Five-sphere Integrated Plan}: Economic construction, political construction, cultural construction, social construction, and ecological civilization construction.
    \item \textbf{Principles for advancing Chinese modernization}: Uphold and strengthen the Party's overall leadership; uphold the path of socialism with Chinese characteristics; uphold the people-centered development philosophy; uphold deepening reform and opening up; and uphold the fighting spirit.
    \item \textbf{Greatest national condition}: The leadership of the Communist Party of China.
    \item \textbf{Strong leadership core of socialism with Chinese characteristics}: The Communist Party of China.
    \item \textbf{Fundamental leadership system}: The system of Party leadership.
    \item \textbf{The Four-pronged Comprehensive Strategy}: Building a modern socialist country in all respects, deepening reform in all respects, governing the country according to law in all respects, and governing the Party with full rigor.
\end{enumerate}

\section{VII. People-Centered Development and Reform}

\begin{enumerate}[leftmargin=2em]
    \item \textbf{Fundamental political stance of the Communist Party of China}: The people's stance.
    \item \textbf{How to uphold the people's stance}: Always remember the Party's original aspiration and mission, maintain close ties with the masses, and love, respect, and stand in awe of the people.
    \item \textbf{Goal of struggle}: The people's aspiration for a better life.
    \item \textbf{The people}: They are the root of the Party's life, the foundation of governance, and the source of strength.
    \item \textbf{Significance of reform and opening up}: It is the crucial move determining contemporary China's destiny, the crucial move for realizing the Two Centenary Goals and national rejuvenation, an important magic weapon enabling the Party and the people to catch up with the times, and the only path to uphold and develop socialism with Chinese characteristics.
    \item \textbf{How to deepen reform comprehensively}: Persist in and improve the Party's leadership and the socialist system with Chinese characteristics; persist in the people-centered approach and promote fairness, justice, and well-being; and further emancipate the mind, develop productive forces, and enhance social vitality.
\end{enumerate}

\section{VIII. New Development Philosophy and Modern Economic System}

\begin{enumerate}[leftmargin=2em]
    \item \textbf{New development philosophy}: Innovation, coordination, green development, openness, and sharing.
    \item \textbf{New development pattern}: Taking the domestic circulation as the mainstay while domestic and international circulations reinforce each other.
    \item \textbf{The ``Two Unswervingly''}: Unswervingly consolidate and develop the public sector of the economy, and unswervingly encourage, support, and guide the development of the non-public sector.
    \item \textbf{Modern economic system}: Build an industrial system led by innovation and coordinated development; a unified, open, competitive, and orderly market system; an income distribution system featuring efficiency and fairness; a coordinated urban-rural regional development system; a green development system; a comprehensive opening-up system; and an economic system that gives full play to the market while enabling the government to better perform its role.
\end{enumerate}

\section{IX. Education, Democracy, and Rule of Law}

\begin{enumerate}[leftmargin=2em]
    \item \textbf{Strategic support for building a modern socialist country}: Education is fundamental, science and technology are key, and talent is the foundation.
    \item \textbf{Fundamental task of education}: Foster virtue through education.
    \item \textbf{Fundamental issue of education}: Whom to cultivate, how to cultivate them, and for whom to cultivate them.
    \item \textbf{Fundamental criterion for educational development}: People's satisfaction.
    \item \textbf{Political development path}: Uphold the organic unity of the Party's leadership, the people's status as masters of the country, and law-based governance.
    \item \textbf{Whole-process people's democracy}: It unifies direct and indirect democracy, process and outcome democracy, procedural and substantive democracy, and people's democracy with the state will.
    \item \textbf{Core meaning of the socialist rule-of-law path with Chinese characteristics}: Uphold Party leadership, uphold the socialist system with Chinese characteristics, and implement the socialist rule-of-law theory with Chinese characteristics.
    \item \textbf{Five principles of the rule-of-law path}: Uphold the leadership of the Communist Party of China, uphold the people-centered approach, uphold equality before the law, combine rule of law with rule of virtue, and proceed from China's realities.
    \item \textbf{Status of the Constitution}: The Constitution is the fundamental law of the state, the general charter for governing the country, the concentrated embodiment of the will of the Party and the people, and the source of the highest legal authority.
    \item \textbf{Building the rule-of-law system}: Accelerate the formation of a complete legal norm system, an efficient implementation system, a strict supervision system, a powerful guarantee system, and a complete system of intra-Party regulations.
    \item \textbf{Layout of building a rule-of-law China}: Advance law-based governance, law-based exercise of state power, and law-based government administration in a coordinated way; promote integrated development of a law-based country, government, and society; and coordinate domestic and foreign-related rule of law.
\end{enumerate}

\section{X. Core Values}

\begin{enumerate}[leftmargin=2em]
    \item \textbf{Core socialist values}: Prosperity, democracy, civility, harmony; freedom, equality, justice, rule of law; patriotism, dedication, integrity, and friendship.
    \item \textbf{The great founding spirit of the Party}: Uphold truth and ideals, practice the Party's original aspiration and mission, fear no sacrifice and fight heroically, remain loyal to the Party, and live up to the people.
\end{enumerate}

\end{document}